|

### 2023-09-14 manuscript/manuscript_1.0.Rmd
Forgot to save some changes

  Biological signals allow individuals to respond appropietly. For example, a 
  signal of fighting hability would allow peers to decide whether to fight 
  another individual. But, what prevents weaklings from faking to be 
  strong? Using a theoretical approach we assess whether learning has 
  a role in maintaining a signal honest. We find that when individuals 
  learn how best to respond to a signal, populations are composed of a 
  mixed of honest and dishonest signals. 
editor_options:
  markdown:
    wrap: 80

>>>>

  Biological signals allow animals to respond appropriately when they compete 
  with each other. For example, a signal of fighting ability would allow 
  individuals to decide whether to fight another individual. But, what prevents 
  weaklings from faking to be strong? Using a theoretical approach, we assess 
  whether learning has a role in maintaining honest signals. We find that when 
  individuals learn how best to respond to a signal, populations evolve to be 
  composed of a mix of honest and dishonest signals.

editor_options:
  markdown:
    wrap: 80
---
